---
title: "assignment 6"
output: github_document
---

# Writing Functions

```{r}
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggplot2)) 
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(singer))
suppressPackageStartupMessages(library(ggmap))
suppressPackageStartupMessages(library(singer)) 
```

##Task 2
__1__
First we extract the data for Canada to work on the code
```{r}
chosen_country <- "Canada"
(chosen_data <- gapminder %>% 
  filter(country == chosen_country))
```
Then we plot the graph of gdp per capita against population
and we can use a polynomial function instead of a linear function to better fit the data. 
```{r}
p <- ggplot(chosen_data, aes(x = pop, y = gdpPercap))
p + geom_point() + geom_smooth(method = 'lm', se = FALSE)
```

We fit the data with a cubic function, and the coefficient of x with different degree is shown: 
```{r}
cub_fit <- rlm(gdpPercap ~ year+I(year^2)+I(year^3),chosen_data)
coef(cub_fit)
```
we can then use then plot the cubic function 
```{r}
 curve(predict(cub_fit,data.frame(year=x)),col='blue',lwd=2) 
```


Then we now sum up the above codes to become a function and try out the data above:
with the below function, by inputing the corresponding country name, we could get the cubic regression for the gdp per capita against population for this country.

```{r}
cubic_curve_fit  <-  function (chosen_country){
  chosen_data <- gapminder %>% 
  filter(country == chosen_country)
  
  fit_curve <- rlm(gdpPercap ~ year+I(year^2)+I(year^3), chosen_data)
  setNames(coef(fit_curve),c("intercept","x","x^2","x^3"))
}

cubic_curve_fit("Canada")
```

Again we can try to use this on other countries:
```{r}
cubic_curve_fit("France")
cubic_curve_fit("Afghanistan")
cubic_curve_fit("Japan")
```


## Task 4 Work With the `singer` data

__Use purrr to map latitude and longitude into human readable information on the band’s origin places.__

First, we use head() function to visulise the singer_location dataframe. We realised that there are quite a lot of `NA` appeared in the entry. We need to get rid of these before tidy up the data. 
```{r}
head(singer_locations)
```
```{r}
tidy_data <- singer_locations %>% 
  filter(!is.na(latitude)|!is.na(longitude)|!is.na(city)) %>% 
  dplyr::select(name,city,longitude,latitude)
# while we load the library MASS together with the dplyr, we need to use dplyr::select to call this function
head(tidy_data) %>% 
  knitr::kable()
```
next we are going to map the longitude and latitude to the band's origin place, and the function used in the mapping is `map2()` and the `revgeocode()` from `ggmap` is used to reverse a geo code location using Google Maps.
```{r}

# location <- map2_chr(tidy_data$longitude[30:100],tidy_data$latitude[30:100], ~revgeocode(as.numeric(c(.x,.y)), output ="more" , source = "google"))
```


